Exploratory data analysis

### 2019-07-01 analysis/eda.Rmd
misc
wflow_publish(knitr_in("analysis/eda.Rmd"), view = FALSE, verbose = TRUE)

  fv_nri_info.gain5, fv_nri_info.gain10,
  fv_nri_info.gain15, fv_nri_info.gain20,
  fv_nri_info.gain25, fv_nri_info.gain30
)
library("DataExplorer")
library("dplyr")
library("ggsci")
library("ggplot2")
library("rgdal")
```

@@

```{r eda-19, echo = FALSE}
# file_move("docs/figure/eda.Rmd/defoliation-distribution-plot-1.pdf",
#           "code/98-paper/journal/")
```

>>>>

  fv_nri_info.gain5, fv_nri_info.gain10,
  fv_nri_info.gain15, fv_nri_info.gain20,
  fv_nri_info.gain25, fv_nri_info.gain30
)
library("DataExplorer")
library("dplyr")
library("ggsci")
library("ggplot2")
```

@@

```{r eda-19, echo = FALSE}
file_move("docs/figure/eda.Rmd/defoliation-distribution-plot-1.pdf",
          "code/98-paper/journal/")
```
